Consistent Polyhedral Surrogates via Embedding

### 2019-10-25 notes/top-k.tex
Visiting Raf's comments in top k notes

\begin{lemma}\label{lem:extra-elts-zero}
  \raf{This statement seems off.  I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
	For all $y \in \Y$, there is a minimizer $u$ of $L^{top-k}(\cdot)_y$ satisfying Assumption~\ref{assum:ordered-u} such that $u_{k+1} = \ldots = u_{n-1} = u_n = 0$.
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{k+1} = 0$.
	With Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.

@@

	Since, $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
	Therefore, if $u$ minimizes $L^{top-k}$, so does $u'$.
\end{proof}

@@

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.  Then we can say $u\in\U$ and forget the assumptions going forward.}

\begin{lemma}\label{lem:get-rid-max-op}
	For all $u$ satisfying Assumptions~\ref{assum:ordered-u},~\ref{assum:nonneg}, and~\ref{assum:top-threshold}, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
\end{lemma}
This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.
\begin{proof}
	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$.
	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.

@@

	If $u_y \in [0,1]$, then $(u-e_y)_{[k]} = u_{k+1} = 0$ by Assumption~\ref{assum:nonneg}.
	This yields
	\begin{align*}
	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{u_y}{k}~.~
	\end{align*}
	In this case, $u_y = \min(u_y, 1)$ is subtracted from $1 - u_y + \bar u$.

	If $u_y > 1$, then $(u-e_y)_{[k]} >\geq 0$, and $(u_y - 1)$ is part of the summation.
	This yields
	\begin{align*}
	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{1}{k}~,~
	\end{align*}
	where, as in the above case, $1 = \min(u_y, 1)$, and this is again the term subtracted from $1 - u_y + \bar u$.

@@

\begin{theorem}\label{thm:finite-set}
	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
	For all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
	\begin{align*}
	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
	\end{align*}
	\jessie{Check the $|H|+|M| \leq k$ condition. Worst case, the set $\R$ is still finite without it.}\raf{follows from assump~\ref{assum:nonneg}, no?}
\end{theorem}
\begin{proof}[Proof Sketch.]
%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
	Since $L^{top-k}$ is linear on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
	We know that the size of $H \cup M$ must be less than or equal to $k$ by \jessie{???}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
	Note that if $c = 1$, then we can say $H = \emptyset$.

>>>>

\begin{lemma}\label{lem:extra-elts-zero}
%  \raf{This statement seems off.  I think you want to say that for all $u\in\reals^d$, there is a $u'$ satisfying assumption~\ref{assum:nonneg} such that $L(u')_y \leq L(u)_y$ for all $y$ (pardon lazy notation).}
	For all $u \in \reals^d$ satisfying Assumption~\ref{assum:ordered-u}, there is a $u'$ satisfying Assumption~\ref{assum:nonneg} so that $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$.
\end{lemma}
\begin{proof}
	By Lemma~\ref{lem:invar-ones}, we can fix $u_{k+1} = 0$.
	With Assumption~\ref{assum:ordered-u}, we then have $u_i \leq 0$ for all $i \geq k+1$.
	Consider $u'$ such that $u'_i = u_i$ for all $i$ so that $u_i \geq 0$, and $u'_i = 0$ otherwise.

@@

	As an aside, since $L^{top-k}(u)_y \geq L^{top-k}(u')_y$ for all $y \in \Y$, this also holds for the expected loss for all $p \in \simplex$.
\end{proof}

@@

\section{Re-writing the loss}
The following Lemma allows us to consider the loss without the $(\cdot)_+$ operator.
Before we do so, consider the set $\U$ to be all $u \in \reals^n$ satisfying Assumptions~\ref{assum:ordered-u}, \ref{assum:nonneg}, and ~\ref{assum:top-threshold}.
That is, 
\begin{align*}
\U := \{ u \in \reals^n : \bar u_1 + 1 \geq u_1 \geq u_2 \geq \ldots \geq u_k \geq 0 = u_{k+1} = \ldots = u_n \}~.~
\end{align*}
\jessie{this is wrong... doesn't have $u_2 \leq \bar u_{-2}+1$... at least not trivially.}

\raf{I think it might be handy to introduce the set $\U$ here to be the points satisfying all three assumptions --- maybe explicitly write the constraints and nod to the assumptions.  Then we can say $u\in\U$ and forget the assumptions going forward.}

\begin{lemma}\label{lem:get-rid-max-op}
	For all $u \in \U$, we have $1 -u_y + \frac{1}{k} \sum_{i=1}^k (u - e_y)_{[i]} \geq 0$.
\end{lemma}
This statement allows us to consider the loss $L^{top-k}$ without the $(\cdot)_+$ operator, since the inside term being nonnegative implies the max of the term and $0$ is always the inside term.
\begin{proof}
	First, we have $\frac 1 k \sum_{i=1}^k (u-e_y)_{[i]} \geq 0$ by nonnegativity of the first $k+1$ elements of $u$.
	Moreover, we need to show that $u_y \leq 1 + \frac 1 k \sum_{i=1}^k (u-e_y)_{[i]}$.

@@

	If $u_y \in [0,1]$, then $(u-e_y)_{[k]} = u_{k+1} = 0$ by Assumption~\ref{assum:nonneg}.
	This yields
	\begin{align*}
	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{u_y}{k}~.~
	\end{align*}
	In this case, $u_y = \min(u_y, 1)$, and $\frac {u_y}{k}$ is subtracted from $1 - u_y + \bar u$.

	If $u_y > 1$, then $(u-e_y)_{[k]} \geq 0$, and $(u_y - 1)$ is part of the summation.
	This yields
	\begin{align*}
	L^{top-k}(u)_y &= 1 - u_y + \bar u - \frac{1}{k}~,~
	\end{align*}
	where, as in the above case, $1 = \min(u_y, 1)$, and $\frac{1}{k}$ is the term subtracted from $1 - u_y + \bar u$.

@@

\begin{theorem}\label{thm:finite-set}
	Consider the loss $L^{top-k} : \reals^n \times \Y \to \reals_+$ given in Equation~\ref{eq:top-k-surrogate}.  
	For all $p \in \simplex$, there is a report in the following report set $\R$ minimizing $\inprod{p}{L^{top-k}(\cdot)}$.
	\begin{align*}
	\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
	\end{align*}
\end{theorem}
\begin{proof}[Proof Sketch.]
%	The above work tells us that when $p_y > \frac 1 {k+1}$, it is optimal to set $u_y > 0$, and otherwise, it is optimal to set $u_y = 0$.
	Since $L^{top-k}$ is linear on $[0,1]$ and $[1, c]$ for some $c \geq 1$ and all dimensions $i \in [n]$, we know that the optimum is on the boundary of such reports, so when we bump $u_y$ up to some number greater than $0$, it should either be one $1$ or $c$ to be an optimal report.
	$H$ represents the elements of the report that are bumped up to $c$, and $M$ represents the elements of the report that are bumped up to $1$.
	We know that the size of $H \cup M$ must be less than or equal to $k$ by Assumption~\ref{assum:nonneg}, and $H \cap M$ is empty by each element of $u$ being real-valued, so for $c > 1$, $u_i$ cannot simultaneously be equal to $c$ and $1$, hence the restrictions on $\R$.
	Note that if $c = 1$, then we can say $H = \emptyset$.
